Uppangala tree functionnal traits: Draft

### 2016-06-29 inst/doc/PreliminaryResults.Rmd
v0.1.9015 cosaspect DEMderiv.R #AV

@@

```{r SEM}
library(lavaan)
m1 <- '
Abiotic =~ Slope + Curvature + Wetness + SW
Traits =~ WD.cwm + Thick.cwm + LA.cwm + LDMC.cwm + SLA.cwm
Biotic =~ BA + Canopy
Traits ~ Abiotic + Biotic
'
m2 <- '
Abiotic =~ Slope + Curvature + Wetness + SW
Traits =~ WD.cwm + Thick.cwm + LA.cwm + LDMC.cwm + SLA.cwm
Biotic =~ BA + Canopy
Biotic ~ Traits + Abiotic
'
fit1 <- sem(m1, data = com$abundance@data)
fit2 <- sem(m2, data = com$abundance@data)
semPlot::semPaths(fit1,what='path',whatLabels='std',intercept=FALSE,residuals=FALSE,thresholds=FALSE,nCharNodes=0,nCharEdges=0,groups='manlat',pastel=TRUE,title=TRUE,curveAdjacent=TRUE,ask=FALSE)
```

>>>>

```{r RLQ2, eval=FALSE, include=FALSE}
library(ade4)

# Matrices
Lm <- data.frame(tapply(rep(1, length(Trees[,1])), list(Trees$com, Trees$SpCode), sum))
# Lm <- data.frame(tapply(Trees$`2013_girth`/2*pi, list(Trees$com, Trees$SpCode), sum)) #BA
Lm[is.na(Lm)] <- 0
Qm <- PFT_sp[c('SLA', 'LDMC', 'WD', 'Thick', 'LA')]
row.names(Qm) <- PFT_sp$Sp_Code
Qm <- Qm[-which(is.na(Qm$WD)),]
Qm <- Qm[names(Lm),]
Rm <- com@data[c('Slope', 'Curvature', 'Wetness', 'SW', 'Canopy', 'BA')]
row.names(Rm) <- com@data$id

# Consistency
all(row.names(Lm) == row.names(Rm))
all(row.names(Lm) %in% row.names(Rm))
Lm <- Lm[row.names(Rm),]
all(names(Lm) == row.names(Qm))
Qm <- Qm[names(Lm),]
Qm <- Qm[-which(is.na(Qm$WD)),]
Lm <- Lm[row.names(Qm)]
Lm[Lm > 0] <-  1 #Presence-absence
Lm <- Lm / rowSums(Lm)

# RLQ
L <- dudi.coa(Lm, scannf = F)
R <- dudi.pca(Rm, scannf = F, row.w = L$lw)
Q <- dudi.pca(Qm, scannf = F, row.w = L$cw)
rlq <- rlq(R, L, Q, scannf = F)
model = 6
rd <- randtest(rlq, modeltype = model)
fq <- fourthcorner.rlq(rlq, type = "Q.axes", modeltype = model)
fr <- fourthcorner.rlq(rlq, type = "R.axes", modeltype = model)
fqr <- fourthcorner(Rm, Lm, Qm, modeltype = model)
fqr.adj <- p.adjust.4thcorner(fqr, p.adjust.method.G = "fdr", p.adjust.method.D = "fdr")

# Results
summary(rlq)
plot(rlq)
s.arrow(rlq$l1)
s.arrow(rlq$c1)
s.label(rlq$lQ, boxes = FALSE)
rd
plot(rd)
alpha = 0.5
plot(fq, alpha = alpha, stat = "D2")
plot(fr, alpha = alpha, stat = "D2")
plot(fqr.adj, alpha = alpha, stat = "D2")
plot(fqr.adj, x.rlq = rlq, alpha = alpha, stat = "D2", type = "biplot")
```

@@

```{r SEM}
library(lavaan)
m1 <- '
Abiotic =~ Slope + Curvature + Wetness + SW
Traits =~ WD.cwm + Thick.cwm + LA.cwm + LDMC.cwm + SLA.cwm
Biotic =~ BA + Canopy
Traits ~ Abiotic + Biotic
'
m2 <- '
Abiotic =~ Slope + Curvature + Wetness + SW
Traits =~ WD.cwm + Thick.cwm + LA.cwm + LDMC.cwm + SLA.cwm
Biotic =~ BA + Canopy
Biotic ~ Traits + Abiotic
'
fit1 <- sem(m1, data = com$abundance@data)
fit2 <- sem(m2, data = com$abundance@data)
semPlot::semPaths(fit1,
                  what = 'col',
                  whatLabels = 'std',
                  style = 'lisrel',
                  residuals = T,
                  nCharNodes = 0,
                  nCharEdges = 0,
                  groups='manlat',
                  pastel = T,
                  ask = F)
```

### 2016-06-29 inst/doc/draft.Rmd
v0.1.9015 cosaspect DEMderiv.R #AV

---
title: "Uppangala tree functionnal traits: Draft"
author: "Sylvain Schmitt"
date: "`r Sys.Date()`"
output: pdf_document
bibliography: refs.bib
---

>>>>

---
title: 'Uppangala tree functionnal traits: Draft'
author: "Sylvain Schmitt"
date: '`r Sys.Date()`'
output: pdf_document
bibliography: refs.bib
---
